---
title: "project1_reproducible_research"
output: html_document
---

This is the first project for coursera's Reproducible Research Class

The first step is to download the data

```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv")
names(activity)

```
We are now interested in visualizing the number of steps taken every day
```{r}
library(plyr)
stepsPerDay <- ddply(activity, c("date"), summarize, totsteps=sum(steps, na.rm=TRUE))
hist(stepsPerDay$totsteps)
mean(stepsPerDay$totsteps)
median(stepsPerDay$totsteps)
```
We will now make a plot for the time series plot to track activity throughout the day

```{r}
avgStepsPerInterval <- ddply(activity, c("interval"), summarize, totsteps=sum(steps, na.rm=TRUE))
intervalCounts <- count(activity$interval)
names(intervalCounts)
avgStepsPerInterval$intervalFreq <- intervalCounts$freq
avgStepsPerInterval$avgsteps <- with(avgStepsPerInterval, totsteps/intervalFreq)
head(avgStepsPerInterval)
plot(avgStepsPerInterval$interval, avgStepsPerInterval$avgsteps, type="l")
avgStepsPerInterval[avgStepsPerInterval$avgsteps == max(avgStepsPerInterval$avgsteps),]
```
Interval 835 has the highest number of average steps

Now we will count the NA's and replace them with appropriate data
```{r}
missingValues <- activity[activity$steps == NA,]
nrow(missingValues)
```